Automatic Visual Inference for Linear Regression

### 2023-04-11 Milestone_presentation_2/Milestone_presentation_2/Milestone_presentation_2.Rmd
init the M2 presentation folder

.caption[
Fig. 3: _A Roberts loom in a weaving shed in 1835 and a Watt steam engine._ 
]

@@

#### Due to limited computing resources, we apply **transfer learning** to train five computer vision models.

@@

#### Due to limited computing resources, we apply **transfer learning** to train five computer vision models.

#### Five **pre-trained models** are used, including **VGG16**, **VGG19**, **Xception**, **ResNet152V2** and **InceptionV3**.

@@

#### Model is trained with **Tensorflow** and **Keras**.

@@

#### Deploy the automatic visual inference as an online aplication

@@

# References

@@

@@

>>>>

@@

#### Due to limited computing resources, we apply **transfer learning** `r BibOptions(max.names = 1);Citep(myBib, "weiss_survey_2016")` to train five computer vision models.

@@

#### Due to limited computing resources, we apply **transfer learning** `r BibOptions(max.names = 1);Citep(myBib, "weiss_survey_2016")` to train five computer vision models.

#### Five **pre-trained models** are used, including **VGG16** `r BibOptions(max.names = 5);Citep(myBib, "simonyan_very_2015")`, **VGG19** `r BibOptions(max.names = 5);Citep(myBib, "simonyan_very_2015")`, **Xception** `r BibOptions(max.names = 5);Citep(myBib, "chollet_xception_2017")`, **ResNet152V2** `r BibOptions(max.names = 1);Citep(myBib, "he_identity_2016")` and **InceptionV3** `r BibOptions(max.names = 1);Citep(myBib, "szegedy_rethinking_2015")`.

@@

#### Models are trained with **Tensorflow** and **Keras**.

@@

#### Deploy the automatic visual inference as an online aplication.

@@

# Bibliography

@@

Chollet, F. (2017). “Xception: Deep Learning with
Depthwise Separable Convolutions”. In:
_arXiv:1610.02357 [cs]_. arXiv: 1610.02357. URL:
[http://arxiv.org/abs/1610.02357](http://arxiv.org/abs/1610.02357).

@@

He, K. et al. (2016). “Identity Mappings in Deep
Residual Networks”. In: _arXiv:1603.05027 [cs]_. URL:
[http://arxiv.org/abs/1603.05027](http://arxiv.org/abs/1603.05027).

Simonyan, K. et al. (2015). “Very Deep Convolutional
Networks for Large-Scale Image Recognition”. In:
_arXiv:1409.1556 [cs]_. URL:
[http://arxiv.org/abs/1409.1556](http://arxiv.org/abs/1409.1556).

Szegedy, C. et al. (2015). “Rethinking the Inception
Architecture for Computer Vision”. In:
_arXiv:1512.00567 [cs]_. URL:
[http://arxiv.org/abs/1512.00567](http://arxiv.org/abs/1512.00567).

Weiss, K. et al. (2016). “A survey of transfer
learning”. En. In: _Journal of Big Data_ 3.1, p. 9.
ISSN: 2196-1115. DOI:
[10.1186/s40537-016-0043-6](https://doi.org/10.1186%2Fs40537-016-0043-6).
URL:
[http://journalofbigdata.springeropen.com/articles/10.1186/s40537-016-0043-6](http://journalofbigdata.springeropen.com/articles/10.1186/s40537-016-0043-6).
